Algorithm explanation

### 2013-08-26 article/thesis.tex
Change filename
Bibliography

\documentclass[master,final,11pt]{iscs-thesis}

@@

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage{syntax}

@@

One of the most common methods of such abstraction is predicate
abstraction.  An automated theorem prover finds appropriate predicates
for specific program locations.  An execution state at each location
is then expressed by a Boolean valuation of the given predicates.  If
the abstraction is too coarse and a model checker discovers an
infeasible error execution path in an abstract system, the prover
computes an additional predicate at a specific program location to
refine the abstraction.  The additional predicate must be satisfied at
the location under the execution in the concrete model along the
discovered path, and the execution does not lead to the program
failure by the same path.  After the refinement, the infeasible path
is ruled out and no longer found by the model checker.

@@

Among various program verification techniques, when software model
checking with predicate abstraction is adopted, the interpolation is
used to compute the abstraction predicate along a spurious
counterexample that a model checker discovered.  It is done by
computing a Craig's interpolant between the strongest postcondition at
the location and the weakest precondition to the failure point at
every program location.

However, by the existing interpolating theorem prover, we may not be
able to obtain a simple solution.  Consider the example below.
\begin{align*}
\varphi_1 : (x = 0 \wedge y = 0) \vee (x = 1 \wedge y = 1) \\
\varphi_2 : (x \neq 0 \wedge y = 0) \vee (x \neq 1 \wedge y = 1)
\end{align*}
Although one may be able to obtain $x = y$ as the simplest
interpolation between $\varphi_1$ and $\varphi_2$, CSIsat\cite{csisat}
returns
\[ TODO \]
as a solution.

@@

\subsection{Example}

@@

\subsection{Preliminaries}

Our algorithm aims to compute a Craig's interpolant over linear
arithmetic formulas.

\paragraph{Craig's Interpolation}
Given two logical formulas $A$ and $B$ that are inconsistent each
other, we call a new preposition $I$ a Craig's interpolant between $A$
and $B$ such that $I$ is implied by $A$ and inconsistent with $B$.
$I$'s vocabulary must be only free variables that appears in both $A$
and $B$.

@@

\subsection{Algorithm}

@@

\subsection{Preliminaries}

@@

\subsection{Simple solution}

@@

\subsection {Graph transformation}

@@

>>>>

\documentclass[master,final,12pt]{iscs-thesis}

@@

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage{syntax}
\usepackage{url}

@@

One of the most common methods of such abstraction is predicate
abstraction\cite{DBLP:conf/cav/GrafS97}.  An automated theorem prover
finds appropriate predicates for specific program locations.  An
execution state at each location is then expressed by a Boolean
valuation of the given predicates.  If the abstraction is too coarse
and a model checker discovers an infeasible error execution path in an
abstract system, the prover computes an additional predicate at a
specific program location to refine the abstraction.  The additional
predicate must be satisfied at the location under the execution in the
concrete model along the discovered path, and the execution does not
lead to the program failure by the same path.  After the refinement,
the infeasible path is ruled out and no longer found by the model
checker.

@@

Among various program verification techniques, when software model
checking with predicate abstraction is adopted, the interpolation is
used to compute the abstraction predicate along a spurious
counterexample that a model checker discovered.  It is done by
computing a Craig interpolant between the strongest postcondition at
the location and the weakest precondition to the failure point at
every program location.

However, by the existing interpolating theorem prover, we may not be
able to obtain a simple solution.  Consider the example below.
\begin{align*}
\varphi_1 : (x = 0 \wedge y = 0) \vee (x = 1 \wedge y = 1) \\
\varphi_2 : (x \neq 0 \wedge y = 0) \vee (x \neq 1 \wedge y = 1)
\end{align*}
Although one may be able to obtain $x = y$ as the simplest
interpolation between $\varphi_1$ and $\varphi_2$,
CSIsat\cite{DBLP:conf/cav/BeyerZM08} returns
\[ TODO \]
as a solution.

@@

\section{Example}

@@

\section{Preliminaries}

Our algorithm aims to compute a Craig interpolant over linear
arithmetic formulas.

\paragraph{Craig Interpolation}
Given two logical formulas $A$ and $B$ that are inconsistent each
other, we call a new preposition $I$ a \emph{Craig interpolant}
\cite{DBLP:journals/jsyml/Craig57} between $A$ and $B$ such that $I$
is implied by $A$ and inconsistent with $B$.  $I$'s vocabulary must be
only free variables that appears in both $A$ and $B$.  If $A \wedge B$
is unsatisfiable, an interpolant $I$ always exists.

@@

\section{Algorithm}

@@

\section{Preliminaries}

@@

\section{Simple solution}

@@

\section {Graph transformation}

@@

\chapter{Related work}

Lorem ipsum
\cite{DBLP:journals/jsyml/Craig57}
\cite{DBLP:conf/cav/GrafS97}
\cite{DBLP:conf/cav/McMillan03}
\cite{DBLP:conf/popl/HenzingerJMM04}
\cite{DBLP:journals/tcs/McMillan05}
\cite{DBLP:conf/tacas/McMillan05}
\cite{DBLP:conf/tacas/JhalaM06}
\cite{website:foci}
\cite{DBLP:conf/tacas/AmlaM07}
\cite{DBLP:conf/pldi/BeyerHMR07}
\cite{DBLP:journals/sttt/BeyerHJM07}
\cite{DBLP:conf/vmcai/RybalchenkoS07}
\cite{DBLP:conf/cav/BeyerZM08}
\cite{DBLP:conf/ppdp/UnnoK09}
\cite{DBLP:conf/cav/Rybalchenko10}
\cite{DBLP:conf/popl/GuptaPR11}
\cite{DBLP:conf/pldi/KobayashiSU11}
\cite{DBLP:conf/aplas/GuptaPR11}
\cite{DBLP:conf/pepm/SatoUK13}
\cite{DBLP:conf/sas/BjornerMR13}
\cite{DBLP:conf/cav/DaiXZ13}
\cite{DBLP:conf/cav/RummerHK13}
\cite{DBLP:conf/cav/AlbarghouthiM13}
\cite{DBLP:conf/cav/BeyenePR13}.
